Effective collector efficiency of sparse and dense arrays of emergent cylindrical collectors in laminar-turbulent transitional flows

### 2020-10-19 workingdraft/draft.tex

Effective collector efficiency was found to decrease with increasing collector Reynolds number and collector density in nearly all cases (Figure \ref{fig:ece}). One exception occurred at the lowest collector density ($\phi_c = 0.22\%$), where the intermediate $\Rey_c$ treatment ($\Rey_c = 134$) had lower ECE than both the lower and higher $\Rey_c$ treatments (Figure \ref{fig:ece}a). When compared to the other collector density treatments with the same $\Rey_c$ value, this low collector-density experiment's calculated ECE was slightly lower than the intermediate collector-density treatment, and was greater than the highest collector-density treatment (Figure \ref{fig:ece}b). For both of these comparisons, the large magnitude of our uncertainty suggests that the mid-$\Rey_c$, low-collector-density result could simply be an experimental anomaly.

@@

Monte Carlo analysis determined that there is a significant (null hypothesis: $\mu = 0$) negative relationship between ECE and collector density for the low (p = 0.004) and high (p = 0.019) $\Rey_c$ treatments, but no significant effect was detected (p > 0.05) for the intermediate treatment (Figure \ref{fig:monte}a). This approach also found a significant negative relationship between ECE and $\Rey_c$ for the low (p = 0.026) and high (p = 0.046) collector density treatments, but an insignificant (p > 0.05) trend for the intermediate collector density treatment (Figure \ref{fig:monte}b).

@@

\begin{table}[H]
\caption{Turbulence and flow characteristics for all collector solid volume fraction ($\phi_c$) and $\Rey_c$ treatments, including the control (zero-collector) treatments for reference.}
\centering
%% \tablesize{} %% You can specify the fontsize here, e.g., \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{>{\bfseries}r>{\bfseries}rrr}
\toprule
\textbf{$\phi_c$}&\textbf{$\Rey_c$}&\textbf{Turbulent Kinetic Energy (\SI{}{\metre^2/\second^2})}&\textbf{Bed Shear Stress (\SI{}{\pascal})}\\
\midrule
Control &   67  & \num{2.48d-6}&\num{-5.52d-4}\\
        &   134 & \num{2.98d-6}&\num{ 3.17d-3}\\
        &   200 & \num{3.37d-6}&\num{ 5.13d-3}\\
\midrule
0.22\% &   67  & \num{1.23d-6}&\num{-2.95d-5}\\
        &   134 & \num{5.26d-6}&\num{-1.39d-4}\\
        &   200 & \num{1.22d-5}&\num{ 1.87d-2}\\
\midrule
0.64\% &   67  & \num{9.13d-6}&\num{ 9.62d-4}\\
        &   134 & \num{3.59d-5}&\num{ 1.20d-3}\\
        &   200 & \num{5.96d-5}&\num{ 6.52d-4}\\
\midrule
1.17\%  &   67  & \num{1.11d-5}&\num{ 4.47d-4}\\
        &   134 & \num{2.98d-5}&\num{ 1.36d-3}\\
        &   200 & \num{5.44d-5}&\num{ 2.44d-3}\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}[H]
\centering
\includegraphics[width=5in]{../pics/cphiplot.png}
\caption{A comparison of the C values calculuated for each of our collector-density treatments to those calculated by Fauria et al. \cite{Fauria_2015}. The black line represents the power law model of best fit between C and collector solid volume fraction ($\phi_c$) for our collector density treaments and those of Fauria et al. combined (n = 5), for which R$^2$ = 0.82.}
\label{fig:cphi}
\end{figure}

>>>>

Effective collector efficiency was found to decrease with increasing collector Reynolds number and collector density in nearly all cases (Figure \ref{fig:ece}). One exception occurred at the lowest collector density ($\phi_c = 0.22\%$), where the intermediate $\Rey_c$ treatment ($\Rey_c = 134$) had lower ECE than both the lower and higher $\Rey_c$ treatments (Figure \ref{fig:ece}a). When compared to the other collector-density treatments with the same $\Rey_c$ value, this low collector-density experiment's calculated ECE was slightly lower than the intermediate collector-density treatment, and was greater than the highest collector-density treatment (Figure \ref{fig:ece}b). For both of these comparisons, the large magnitude of our uncertainty suggests that the mid-$\Rey_c$, low-collector-density result could simply be an experimental anomaly.

@@

Monte Carlo analysis determined that there is a significant (null hypothesis: $\mu = 0$) negative relationship between ECE and collector density for the low (p = 0.004) and high (p = 0.019) $\Rey_c$ treatments, but no significant effect was detected (p > 0.05) for the intermediate treatment (Figure \ref{fig:monte}a). This approach also found a significant negative relationship between ECE and $\Rey_c$ for the low (p = 0.026) and high (p = 0.046) collector-density treatments, but an insignificant (p > 0.05) trend for the intermediate collector-density treatment (Figure \ref{fig:monte}b).

@@

\begin{table}[H]
\caption{Turbulence and flow characteristics for all collector solid volume fraction ($\phi_c$) and $\Rey_c$ treatments, including the control (zero-collector) treatments for reference.}
\centering
%% \tablesize{} %% You can specify the fontsize here, e.g., \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{>{\bfseries}r>{\bfseries}rrr}
\toprule
\textbf{$\phi_c$}&\textbf{$\Rey_c$}&\textbf{Turbulent Kinetic Energy (\SI{}{\metre^2/\second^2})}\\
\midrule
Control &   67  & \num{2.48d-6}\\
        &   134 & \num{2.98d-6}\\
        &   200 & \num{3.37d-6}\\
\midrule
0.22\% &   67  & \num{1.23d-6}\\
        &   134 & \num{5.26d-6}\\
        &   200 & \num{1.22d-5}\\
\midrule
0.64\% &   67  & \num{9.13d-6}\\
        &   134 & \num{3.59d-5}\\
        &   200 & \num{5.96d-5}\\
\midrule
1.17\%  &   67  & \num{1.11d-5}\\
        &   134 & \num{2.98d-5}\\
        &   200 & \num{5.44d-5}\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}[H]
\centering
\includegraphics[width=5in]{../pics/cphiplot.png}
\caption{A comparison of the C values calculuated for each of our collector-density treatments to those calculated by Fauria et al. \cite{Fauria_2015}. The black line represents the power law model of best fit between C and collector solid volume fraction ($\phi_c$) for our collector-density treaments and those of Fauria et al. combined (n = 5), for which R$^2$ = 0.82.}
\label{fig:cphi}
\end{figure}
